%
%\documentclass[Journal]{ascelike}
% \documentclass[Proceedings]{ascelike}
\documentclass[Preprint,10pt]{ascelike}
%
% Jan. 30, 2025
%
% include this line for producing ASCE-sytle citations and bibliography
\usepackage{biblatex}
% !!! Note that you should use "biber", not "bibtex", to process the citations.
%
% state your bibliographic ".bib" databases here.  Include the suffix ".bib".
\addbibresource{ascexmpl.bib}
%
% the following are some useful packages, but it's your choice
%
% handling graphics in figures
\usepackage{graphicx}
%
% AMS macros and fonts
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsbsy}
%
% the booktabs package, for nicer tables
\usepackage{booktabs}
  \setlength\heavyrulewidth{1.5pt}
  \setlength\lightrulewidth{1.0pt}
  \setlength\abovetopsep{0pt}
  \setlength\belowrulesep{0pt}
%
% to use hyperlinks within pdf document (with pdflatex, not latex):
%\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
%
% NOTE: Don't include the \NameTag{<your name>} if you have selected
%       the NoPageNumbers option: this leads to an inconsistency and
%       a warning, and the NameTag is ignored.
\NameTag{Ma \emph{et al}, \today}
%
%
\begin{document}
%
% with Journal, manually make first letters uppercase
\title{3D printed Warren truss bridge inspired by the Kingston-Rhinecliff Bridge}
%
% enter authors and affiliations in the manner of the authblk.sty package.
% Authors' [*] are matched with affiliations' [*]
\author[1]{Finn Blair}
\author[1]{Avvin Budhiraja}
\author[1]{Michael Christie}
\author[1]{Matthew Henkel}
\author[1]{Brandon Ma}
\author[1]{Nikita Parkhomovsky}
\author[1]{Liam Pladl}
\author[1]{Vedant Umesh}
\affil[1]{Science \& Engineering Magnet Program,
          Manalapan High School, 20 Church Lane,
          Englishtown, NJ 07726. E-mail: 428bma@frhsd.com.}
%
% you must process the title and authors
\maketitle
%
\begin{abstract}
This project explores the effectiveness of Warren truss bridge design, inspired by the structural efficiency of the Kingston-Rhinecliff Bridge and our Nintendo Switch-inspired connectors. Warren trusses are known for their ability to distribute loads effectively through triangulated diagonals, making them a highly favorable option. We used a slide-lock and dovetail joint system to enable sections to be within the required dimensions while allowing for quick assembly. We developed our design using CAD and performed an initial analysis for static loads using finite element methods in Onshape.
\end{abstract}
%
% for the Preprint option, the next line creates two-column documents.
% You can leave the line here, even if you don't use the Preprint option
\ifthenelse{\boolean{Preprint}}{\begin{multicols}{2}}{}
%
% this begins the document's text
\section{Introduction}\label{sec:Introduction}
Blah blah. 

\section{Design}
\subsection{Print details}

\section{Results}

\section{Discussion}
\subsection{Challenges faced}
\subsection{Potential improvements}

\section{Acknowledgements}
We thank E. Levin, J. Philhower, J. Powers, E. Kaplan, L. Stelljes, J. Komitas, Prof. Hickey and Ms.
Botei, Dr. Evangelista. We acknowledge support from the Manalapan High School Science \& Engineering Magnet Program.

\section{Author contributions}
List what each guy did. 

%
% Here, we use "\printbibliography" to create an "*.aux" file that can be
% processed with biber, using the stylefiles, ascelike.bbx and ascelike.cbx
\printbibliography
%
%
% the next line is for the Preprint option, for a two-column preprint. You
% can leave the line here, even if you don't use the Preprint option
\ifthenelse{\boolean{Preprint}}{\end{multicols}}{}
%
\end{document}
